Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-06-12 manuscript.tex
complie test on windows; minor change

\begin{IEEEkeywords}
    Neuro-adaptive control, constrained optimization, deep neural network, input constraint.
\end{IEEEkeywords}

@@

We consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq +\rbVm \dq+ \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM \ddtt \fe
        +
        \tfrac{1}{2}\fe^\top \ddtt{\rbM}\fe
        \\
        =&
        \fe^\top 
        \left(
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        \right)
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \ddtt{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top 
        \left(
            \mv f
            -\rbd
            +\mysat(\rbu)
        \right)
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\ddtt{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))\\
        % \\
        % \le&
        % -\lambda_{\min}(\mm K)\norm{\fe}^2
        % +
        % \overline\tau_d\norm{\fe}
        % +
        % \fe^\top (\mysat(\rbu)-\rbu^*)
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation} 
Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped system uncertainty $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
Hence, the ideal control input $\rbu^*$ is defined as $-\mv f$.
However, $\rbu^*$ is not available in practice, since system dynamics encapsulated in $\mv f$ are unknown.

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i, \forall i\in \{0,\cdots,k\}$ as 
\begin{equation}
    \wth := 
    \begin{pmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{pmatrix}
    =
    \begin{pmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{pmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. 
The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ can be obtained using Proposition \ref{propsit:kron} and the chain rule as follows:
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq:gradient:phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (
            \mm I_{l_{k+1}}
            \otimes 
            \act_{k}^\top  
        )
        , 
        &
        i=k
        ,
        \\
        \wV_k^\top\act_{k}' 
        (
            \mm I_{l_{k}}
            \otimes  
            \act_{k-1}^\top  
        )
        , 
        & 
        i=k-1
        ,
        \\
        &
        \vdots 
        \\
        \wV_k^\top\act'_{k} 
        \cdots 
        \wV_1^\top\act_1' 
        (
            \mm I_{l_1}
            \otimes 
            {\q}_n^\top  
        )
        , 
        &
        i = 0
        ,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \ddtfrac{\act_i}{\NN_{i-1}}$.

@@

First, weight norm constraints are essential to prevent the weights from diverging during the adaptation process.
The weight norm constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    \left(
        \Vert \estwth_i\Vert^2 
        -
        \overline\theta_i^2 
    \right)    
    % \le 0
    \label{eq:cstr:weight:ball}
\end{equation}
with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$, and the arguments of $c_{\theta_i}(\cdot)$ are omitted for brevity.
The gradient of $\mv{c}_\theta:=\mv c_{\theta}(\estwth)$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j,
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}

@@

The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, with respect to $\estwth_i$ is represented as
\begin{equation}
    \pptfrac{c_j}{\estwth_i} 
    = 
    \pptfrac{c_j}{\rbu} 
    \pptfrac{\rbu}{\estNN} 
    \pptfrac{\estNN}{\estwth_i}
\end{equation}
where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
From the linear mapping in \eqref{eq:linear:map}, $\rbu$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions. 
By Assumption \ref{assum:convex}, the function $c_j$ is convex in $\rbu$-space.
The convex function has a bounded derivative with respect to $\rbu$, since $\rbu$ is a bounded variable (\ie $\pptfrac{c_j}{\rbu}$ is bounded). 
Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in\{k,\cdots,i+1\}$, are bounded. 
This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, is bounded, when $\estwth_i,\ \forall i\in \{k,\cdots,i+1\}$ are bounded.

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        \left(
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        \right)
        \\
        =&
        -\estwth_k^\top 
        \Big(
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        \Big)
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
        }_{=:{\gamma}_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        \underbrace{
            -
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
            }
            \lambda_j 
            \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{=:{\gamma}_2<0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        {\gamma}_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot} and Lemma \ref{lem:stable:set}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            {\gamma}_1
            (
                \overline\tau_d
                +
                \overline\tau
                +
                \bar{\theta}_k\sqrt{l_{k}+1}
                +
                \bar{\epsilon}
            )
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large, due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases sufficiently large, leading to increase in ${\gamma}_2$.
It makes ${\gamma}_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
This drives $\estwth_k$ to the origin until the constraint is satisfied.
By Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in the $\estwth_k$-space.

@@

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link robotic manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
The two-link robotic manipulator actuated by two Cubemars AK10-90 servo motors. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and are illustrated in Fig.~\ref{fig:robot:model}. 
The measured and/or estimated system parameters are provided in Table~\ref{table:system:params}.

@@

% ------------------------------------
% Reference Trajectory
% ------------------------------------
The desired trajectory $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, which satisfy the initial and final joint angles $\mv{x}_1$ and $\mv{x}_2$, as well as zero initial and final joint velocities. 
Here, $t_f$ denotes the duration of each segment.
The desired (reference) trajectory is defined as follows:
\begin{equation}
    \qd(t) 
    =
    \begin{pmatrix}
        {q_d}_1
        \\
        {q_d}_2
    \end{pmatrix}
    =
    \begin{cases}
    \mathcal{P}^5(t;\mv{q}_d^{(0)},\mv{q}_d^{(1)},t_f),
        &
        \text{if } 0 \le t < t_f 
        ,
        \\
    \mathcal{P}^5(t;\mv{q}_d^{(1)},\mv{q}_d^{(2)},t_f),
        &
        \text{if } t_f \le t < 2t_f 
        ,
        \\
    \mathcal{P}^5(t;\mv{q}_d^{(2)},\mv{q}_d^{(1)},t_f),
        & 
        \text{if } 2t_f \le t < 3t_f 
        ,
        \\
    \mathcal{P}^5(t;\mv{q}_d^{(1)},\mv{q}_d^{(0)},t_f),
        &    
        \text{if } 3t_f \le t < 4t_f 
        ,
        \\
    \end{cases}
    \label{eq:desired trajectory}
\end{equation}
where 
$
    \mv{q}_d^{(0)}:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top
$, 
$
    \mv{q}_d^{(1)}:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top
$, 
$
    \mv{q}_d^{(2)}:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top
$, 
and $t_f=3$ s, and the reference trajectory is illustrated in Fig.~\ref{fig:robot:model}.
To demonstrate the learning capability of the DNN, the desired trajectory was applied twice. 
The first and second repetitions of the reference trajectory are referred to as Episode $1$ and Episode $2$, respectively.

>>>>

\begin{IEEEkeywords}DV26H-64YTR-C9WFH-7A33V
    Neuro-adaptive control, constrained optimization, deep neural network, input constraint.
\end{IEEEkeywords}

@@

We consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq +\rbVm \dq+ \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    ,
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM \ddtt \fe
        +
        \tfrac{1}{2}\fe^\top \ddtt{\rbM}\fe
        \\
        =&
        \fe^\top 
        \left(
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        \right)
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \ddtt{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top 
        \left(
            \mv f
            -\rbd
            +\mysat(\rbu)
        \right)
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\ddtt{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))\\
        % \\
        % \le&
        % -\lambda_{\min}(\mm K)\norm{\fe}^2
        % +
        % \overline\tau_d\norm{\fe}
        % +
        % \fe^\top (\mysat(\rbu)-\rbu^*)
        .
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation} 
Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped system uncertainty $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
Hence, the ideal control input $\rbu^*$ is defined as $-\mv f$.
However, $\rbu^*$ is not available in practice, since system dynamics encapsulated in $\mv f$ are unknown.

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i, \forall i\in \{0,\cdots,k\}$ as 
\begin{equation}
    \wth := 
    \begin{pmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{pmatrix}
    =
    \begin{pmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{pmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. 
The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ can be obtained using Proposition \ref{propsit:kron} and the chain rule as follows:
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    ,
    \label{eq:gradient:phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (
            \mm I_{l_{k+1}}
            \otimes 
            \act_{k}^\top  
        )
        , 
        &
        i=k
        ,
        \\
        \wV_k^\top\act_{k}' 
        (
            \mm I_{l_{k}}
            \otimes  
            \act_{k-1}^\top  
        )
        , 
        & 
        i=k-1
        ,
        \\
        &
        \vdots 
        \\
        \wV_k^\top\act'_{k} 
        \cdots 
        \wV_1^\top\act_1' 
        (
            \mm I_{l_1}
            \otimes 
            {\q}_n^\top  
        )
        , 
        &
        i = 0
        ,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \ddtfrac{\act_i}{\NN_{i-1}}$.

@@

First, weight norm constraints are essential to prevent the weights from diverging during the adaptation process.
The weight norm constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    \left(
        \Vert \estwth_i\Vert^2 
        -
        \overline\theta_i^2 
    \right)    
    % \le 0
    ,
    \label{eq:cstr:weight:ball}
\end{equation}
with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$, and the arguments of $c_{\theta_i}(\cdot)$ are omitted for brevity.
The gradient of $\mv{c}_\theta:=\mv c_{\theta}(\estwth)$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j,
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}

@@

The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, with respect to $\estwth_i$ is represented as
\begin{equation}
    \pptfrac{c_j}{\estwth_i} 
    = 
    \pptfrac{c_j}{\rbu} 
    \pptfrac{\rbu}{\estNN} 
    \pptfrac{\estNN}{\estwth_i}
    ,
\end{equation}
where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
From the linear mapping in \eqref{eq:linear:map}, $\rbu$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions. 
By Assumption \ref{assum:convex}, the function $c_j$ is convex in $\rbu$-space.
The convex function has a bounded derivative with respect to $\rbu$, since $\rbu$ is a bounded variable (\ie $\pptfrac{c_j}{\rbu}$ is bounded). 
Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in\{k,\cdots,i+1\}$, are bounded. 
This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, is bounded, when $\estwth_i,\ \forall i\in \{k,\cdots,i+1\}$ are bounded.

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        \left(
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        \right)
        \\
        =&
        -\estwth_k^\top 
        \Big(
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        \Big)
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
        }_{=:{\gamma}_1\in\R_{\ge0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        \underbrace{
            -
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
            }
            \lambda_j 
            \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{=:{\gamma}_2\in\R_{\le0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        {\gamma}_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot} and Lemma \ref{lem:stable:set}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            {\gamma}_1
            (
                \overline\tau_d
                +
                \overline\tau
                +
                \bar{\theta}_k\sqrt{l_{k}+1}
                +
                \bar{\epsilon}
            )
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large, due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\theta_k}^{1}$ shrinks to a point.
The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases sufficiently large, leading to increase in ${\gamma}_2$.
It makes ${\gamma}_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
This drives $\estwth_k$ to the origin until the constraint is satisfied.
By Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in the $\estwth_k$-space.

@@

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link robotic manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
The two-link robotic manipulator actuated by two Cubemars AK10-90 servo motors. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and is illustrated in Fig.~\ref{fig:robot:model}. 
The measured and/or estimated system parameters are provided in Table~\ref{table:system:params}.

@@

% ------------------------------------
% Reference Trajectory
% ------------------------------------
The desired trajectory $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, which satisfy the initial and final joint angles $\mv{x}_1\in\R^2$ and $\mv{x}_2\in\R^2$, as well as zero initial and final joint velocities. 
Here, $t_f$ denotes the duration of each segment.
The desired (reference) trajectory is defined as follows:
\begin{equation}
    \qd(t) 
    =
    \begin{pmatrix}
        {q_d}_1
        \\
        {q_d}_2
    \end{pmatrix}
    =
    \begin{cases}
    \mathcal{P}^5(t;\mv{q}_d^{(0)},\mv{q}_d^{(1)},t_f),
        &
        \text{if } 0 \le t < t_f 
        ,
        \\
    \mathcal{P}^5(t;\mv{q}_d^{(1)},\mv{q}_d^{(2)},t_f),
        &
        \text{if } t_f \le t < 2t_f 
        ,
        \\
    \mathcal{P}^5(t;\mv{q}_d^{(2)},\mv{q}_d^{(1)},t_f),
        & 
        \text{if } 2t_f \le t < 3t_f 
        ,
        \\
    \mathcal{P}^5(t;\mv{q}_d^{(1)},\mv{q}_d^{(0)},t_f),
        &    
        \text{if } 3t_f \le t < 4t_f 
        ,
        \\
    \end{cases}
    \label{eq:desired trajectory}
\end{equation}
where 
$
    \mv{q}_d^{(0)}:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top
$, 
$
    \mv{q}_d^{(1)}:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top
$, 
$
    \mv{q}_d^{(2)}:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top
$, 
and $t_f=3$ s, and the reference trajectory is illustrated in Fig.~\ref{fig:robot:model}.
To demonstrate the learning capability of the DNN, the desired trajectory was applied twice. 
The first and second repetitions of the reference trajectory are referred to as Episode $1$ and Episode $2$, respectively.
